Automated iterative forecasting for the Portal Project

### 2018-01-20 manuscript/portal_iterative_forecasting_ms.Rmd
Add References header

---
title: "Automated iterative forecasting for the Portal Project"
csl: mee.csl
fontsize: 12pt
output:
  pdf_document:
    keep_tex: yes
  html_document: default
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
bibliography: refs.bib
---
\raggedright

@@

>>>>

---
title: "Automated iterative forecasting for the Portal Project"
csl: mee.csl
fontsize: 12pt
output:
  html_document: default
  pdf_document:
    keep_tex: yes
header-includes:
- \usepackage{times}
- \usepackage{setspace}
- \usepackage{booktabs}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
geometry: left=3.5cm, right=3.5cm, top=2.25cm, bottom=2.25cm, headheight=12pt, letterpaper
bibliography: refs.bib
---
\raggedright

@@

# References
